---
title: "Lab 00 - Hello IDS!"
author: "Gavin Liu"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Gavin Liu", "Chun Lian", "Olina Lyu", 
           "member 3", "member 4"),
  github_username = c("mtq4", "Chun515", "Olina-dataS", 
                      "username 3", "username 4"), 
  colour = c("blue", "blue", "blue", 
             "colour 3", "colour 4"),
  hobby = c("game", "sleep", "idk", 
            "idk", "idk"),
  favourite_number = c(2, 8, 4, NA, NA)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


Shows the difference of favorite number for each member

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Insert text here", 
          y = "Insert text here",
          title = "Insert text here")
```

Modify axis, legend, and plot labels


### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

It cannot clearly show the proportion of each person's hobbies, could use pie chart instead of.

